Aneuploidy can be an evolutionary diversion\\ on the path to adaptation

### 2024-01-22 ms/ms.tex
revise effect of ploidy paragraph

% haploids
\paragraph{Effect of ploidy.}
The evolutionary dynamics may change in haploid yeast, in which aneuploidy results in a second, rather than third, chromosome copy. 
For example, it has been demonstrated that in haploid yeast drug resistance mainly evolves via recessive mutations and aneuploidy~\citep{Soncini2020}, whereas in diploid yeast it evolves via dominant mutations, aneuploidy, and gene/segmental duplications~\citep{Barney2021}.
Thus, the second chromosome of disomic yeast may facilitate further adaptation via duplications, rearrangements, and increased mutational tolerance~\citep{Avecilla2023}, while decreasing the chance for adaptation via recessive mutations. 
Future models and experiments can consider this more complex genomic contexts.

>>>>

% haploids
\paragraph{Effect of ploidy.}
The evolutionary dynamics may change in haploid yeast, in which aneuploidy results in a second, rather than third, chromosome copy. 
For example, it has been demonstrated that drug resistance mainly evolves via recessive mutations and aneuploidy in haploid yeast~\citep{Soncini2020}, whereas in diploid yeast it evolves via dominant mutations, aneuploidy, and gene/segmental duplications~\citep{Barney2021}.
Thus, the second chromosome copy of disomic yeast may facilitate further adaptation via duplications, rearrangements, and increased mutational tolerance~\citep{Avecilla2023}, while decreasing the chance for adaptation via recessive mutations. 
Future models and experiments can consider how ploidy and other genomic contexts affect the role of aneuploidy in adaptive evolution.
